\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-30 ase20/eval.tex
Minor edit in Intro and Till Sec. 5.1

We developed \( \tool \) as an open source tool\footnote{The URL of the tool is
anonymized due to a double-blind review process.}, and evaluated the tool
based on the following research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Coverage:} How much parts \( \tool \) automatically extract
the syntax and semantics from ES7 to ES10?
\item RQ2. \textbf{Correctness:} Does \( \tool \) correctly extract IR-based formal
semantics from ECMAScript?
\item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
features ready for inclusion in the next ECMAScript (ES11)?
\end{itemize}

@@

\begin{table}[t]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
\vspace*{-1em}
\small
  \[
    \begin{array}{c?r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \multicolumn{1}{c}{\textbf{Average}}\\\toprule
      \text{\# Lexical productions}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{81}}
      & \inred{\text{78.75}}\\\hline
      \text{\# Syntactic productions}
      & \inred{\text{157}}
      & \inred{\text{167}}
      & \inred{\text{167}}
      & \inred{\text{174}}
      & \inred{\text{166.25}}\\
    \end{array}
  \]
  \[
    \begin{array}{c?r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c?}{\textbf{ES9}}
      & \multirow{2}{*}{\textbf{Average}}\\\cline{1-4}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \\\toprule
      \Delta \; \text{\# Lexical productions}
      & \inred{\text{3}}
      & \inred{\text{5}}
      & \inred{\text{6}}
      & \inred{\text{4.67}}\\\hline
      \Delta \; \text{\# Syntactic productions}
      & \inred{\text{140}}
      & \inred{\text{15}}
      & \inred{\text{8}}
      & \inred{\text{54.33}}\\
    \end{array}
  \]
\end{table}

\( \tool \) targets ECMAScript specifications released after ES7 in 2016 because
our tool utilizes common patterns in the converged writing style since ES7 as
already explained in Section~\ref{sec:overview}.  Thus, we evaluate the coverage
of \( \tool \) by applying it to the most recent four versions of ECMAScript,
ES7 to ES10.  We measured for how many grammar productions and steps in abstract
algorithms \( \tool \) automatically generates parsers and AST-IR translators,
respectively, in two respects: 1) in each version and 2) in each update between
adjacent versions.

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.pdf}
    \caption{Results for existing versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-update.pdf}
    \caption{Results for annual updates}
    \label{fig:semantics-all-version-update}
  \end{subfigure}
  \caption{Number of abstract algorithm steps in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\vspace*{-1em}
\end{figure}

For semantics, Figure~\ref{fig:all-version} shows that \( \tool \) automatically
compile algorithm steps to the corresponding \( \ires \) instructions with
\inred{91.38\%} success rate on average for existing specifications, and
\inred{92.08\%} for updates.  ECMAScript abstract algorithms describe not only
core language semantics but also other helper functions of built-in libraries.
Built-in libraries written in more diverse styles in describing their own
specific functionalities.  Thus, built-in libraries have lower success rates
(\inred{86.74\%} for specifications and \inred{88.24\%} for updates) than core
language semantics (\inred{95.14\%} for specifications and \inred{96.41\%} for
updates).

This results show that \( \tool \) effectively reduces the efforts to
extract the syntax and semantics of JavaScript not only for developing
them from scratch, but also for updating existing ones.

>>>>

We developed \( \tool \) as an open-source tool\footnote{The URL of the tool is
anonymized due to a double-blind review process.}, and evaluated the tool
based on the following research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Coverage:} How much percentage of 
the syntax and semantics does \( \tool \) automatically extract from ES7 to ES10?
\item RQ2. \textbf{Correctness:} Does \( \tool \) extract an IR-based formal
semantics from ECMAScript correctly?
\item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
features ready for inclusion in the next ECMAScript (ES11)?
\end{itemize}

@@

\begin{table}[t]
  \caption{Syntax coverage: Number of productions in each specification
and in each update between adjacent versions,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
\vspace*{-1em}
\small
  \[
    \begin{array}{c?r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \multicolumn{1}{c}{\textbf{Average}}\\\toprule
      \text{\# Lexical productions}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{81}}
      & \inred{\text{78.75}}\\\hline
      \text{\# Syntactic productions}
      & \inred{\text{157}}
      & \inred{\text{167}}
      & \inred{\text{167}}
      & \inred{\text{174}}
      & \inred{\text{166.25}}\\
    \end{array}
  \]
  \[
    \begin{array}{c?r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c?}{\textbf{ES9}}
      & \multirow{2}{*}{\textbf{Average}}\\\cline{1-4}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \\\toprule
      \Delta \; \text{\# Lexical productions}
      & \inred{\text{3}}
      & \inred{\text{5}}
      & \inred{\text{6}}
      & \inred{\text{4.67}}\\\hline
      \Delta \; \text{\# Syntactic productions}
      & \inred{\text{140}}
      & \inred{\text{15}}
      & \inred{\text{8}}
      & \inred{\text{54.33}}\\
    \end{array}
  \]
\end{table}

We evaluated the coverage of \( \tool \) in two respects: syntax
and semantics.  For syntax, we measured how many grammar
productions in specifications \( \tool \) automatically generated
parsers from, and for semantics, we measured how many abstract
algorithm steps in specifications it automatically generated the
JavaScript semantics from.  Because \( \tool \) utilizes common
patterns in the converged writing style since ES7 as we discussed in
Section~\ref{sec:overview}, we evaluated its coverage using the most
recent four versions of ECMAScript, ES7 to ES10.  We measured the
numbers for each ECMAScript version and for each update between
adjacent versions.

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.pdf}
    \caption{For each ECMAScript version from ES7 to ES10}
\vspace*{.5em}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-update.pdf}
    \caption{For each update between adjacent versions}
    \label{fig:semantics-all-version-update}
  \end{subfigure}
\vspace*{-.5em}
\caption{Semantics coverage: Number of algorithm steps in specifications,
from which \( \tool \) generated the semantics}
  \label{fig:all-version}
\vspace*{-1em}
\end{figure}

For semantics, Figure~\ref{fig:all-version} shows that \( \tool \) automatically
compiled algorithm steps to corresponding \( \ires \) instructions with
the success rate of \inred{91.38\%} on average for each ECMAScript version
from ES7 to ES10, and \inred{92.08\%} for each update between adjacent
versions.  ECMAScript abstract algorithms describe not only
core language semantics but also built-in libraries with various helper functions.
Note that built-in libraries are written in more diverse styles than
core language semantics due to their own specific functionalities.
Therefore, built-in libraries have lower success rates
(\inred{86.74\%} for specifications and \inred{88.24\%} for updates) than core
language semantics (\inred{95.14\%} for specifications and \inred{96.41\%} for
updates).

Because \( \tool \) automatically extracts the syntax
and semantics from specifications and updates with high coverage rates,
it reduces efforts not only in developing JavaScript tools from scratch
from specifications but also in evolving existing tools for updates.

### 2020-04-30 ase20/intro.tex
Minor edit in Intro and Till Sec. 5.1

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between the specification written in a
    natural language and tests.}
    To evaluate the correctness of \( \tool \), we checked the extracted
    semantics with the official test conformance suite, Test262~\cite{test262}.
    By manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), we define the \textit{first IR-based formal
    semantics of modern JavaScript}. It fails \inred{XXXX} tests because of the
    specification errors in ES10. We found eight specification errors and
    three of them are even not yet reported errors. They were all confirmed by
    TC39 and will be fixed in the next release.  After fixing them, the formal
    semantics passed all \inred{XX,XXX} applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}

>>>>

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between the specification written in a
    natural language and tests.}
    To evaluate the correctness of \( \tool \), we checked the extracted
    semantics with the official test conformance suite, Test262~\cite{test262}.
    By manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), we defined the \textit{first IR-based formal
    semantics of modern JavaScript}. It failed for \inred{XXXX} tests because of
    specification errors in ES10. Using the tests, we found eight specification errors,
    three of which had not been reported before. They were all confirmed by
    TC39 and will be fixed in the next release.  After fixing them, the formal
    semantics passed all \inred{XX,XXX} applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}
